Gut-resident microorganisms and their genes are associated with cognition and neuroanatomy in children

### 2023-10-23 manuscript/main.tex

\author{%
    \parbox{\linewidth}{\centering
        Kevin S. Bonham,$^{1}$
        Guilherme Fahur Bottino,$^{1}$
        Shelley Hoeft McCann,$^{1}$
        Jennifer Beauchemin,$^{2}$
        Elizabeth Weisse,$^{3}$
        Fatoumata Barry,$^{2}$
        Rosa Cano Lorente,$^{2}$
        The RESONANCE Consortium,
        Curtis Huttenhower,$^{4}$
        Muriel Bruchhage,$^{3}$
        Viren D'Sa,$^{2}$
        Sean Deoni,$^{2}$
        Vanja Klepac-Ceraj$^{1\ast}$
    }
\\
\normalsize{$^{1}$Department of Biological Sciences, Wellesley College, Wellesley, MA, USA}\\
\normalsize{$^{2}$Rhode Island Hospital, Providence, RI, USA}\\
\normalsize{$^{3}$Department of Psychology, University of Stavenger, Stavanger, Norway}\\
\normalsize{$^{4}$Department of Biostatistics, Harvard T.H. Chan School of Public Health, Boston, MA, USA}\\
\\
\normalsize{$^\ast$To whom correspondence should be addressed; E-mail:  vklepacc@wellesley.edu.}
}

>>>>

\author{%
    \parbox{\linewidth}{\centering
        Kevin S. Bonham,$^{1}$
        Guilherme Fahur Bottino,$^{1}$
        Shelley Hoeft McCann,$^{1}$
        Jennifer Beauchemin,$^{2}$
        Elizabeth Weisse,$^{3}$
        Fatoumata Barry,$^{2}$
        Rosa Cano Lorente,$^{2}$
        The RESONANCE Consortium$^{\ast}$,
        Curtis Huttenhower,$^{4}$
        Muriel Bruchhage,$^{3}$
        Viren D'Sa,$^{2}$
        Sean Deoni,$^{2}$
        Vanja Klepac-Ceraj$^{1\dagger}$
    }
\\
\normalsize{$^{1}$Department of Biological Sciences, Wellesley College, Wellesley, MA, USA}\\
\normalsize{$^{2}$Rhode Island Hospital, Providence, RI, USA}\\
\normalsize{$^{3}$Department of Psychology, University of Stavenger, Stavanger, Norway}\\
\normalsize{$^{4}$Department of Biostatistics, Harvard T.H. Chan School of Public Health, Boston, MA, USA}\\
\\
\normalsize{$^\ast$The RESONANCE consortium collaborators and affiliations are listed in the supplementary materials.}\\
\normalsize{$^\dagger$To whom correspondence should be addressed; E-mail:  vklepacc@wellesley.edu.}
}
